Delayed dichromatism as a convenient tool to disentangle the effects of survival and productivity on the population dynamics in waterfowl

### 2024-06-04 Code/Draft_ruddy_duck_vital_rates.Rmd
Data DOI change

\setstretch{1}
```{r vital, fig.cap = "(ref:vital)"}
knitr::include_graphics("../Output/plot_paper_3.png")
```
\setstretch{2}

@@

\setstretch{1}
```{r cor, fig.cap = "(ref:cor)"}
knitr::include_graphics("../Output/plot_paper_4.png")
```
\setstretch{2}

@@

\setstretch{1}

@@

```{r sup, fig.cap = "(ref:sup)"}
knitr::include_graphics("../Output/plot_paper_6.png")
```

@@

\nolinenumbers

>>>>

\setstretch{1}
```{r vital, out.height = "90%", fig.cap = "(ref:vital)"}
knitr::include_graphics("../Output/plot_paper_3.png")
```
\setstretch{2}

@@

\setstretch{1}
```{r cor, out.height = "90%", fig.cap = "(ref:cor)"}
knitr::include_graphics("../Output/plot_paper_4.png")
```
\setstretch{2}

@@

@@

\setstretch{1}
```{r sup, fig.cap = "(ref:sup)"}
knitr::include_graphics("../Output/plot_paper_6.png")
```
\setstretch{2}

@@
